Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2019-07-18 awipev-CO2.Rmd
ph plots updated

seafet_calc_contros_xts <- dplyr::select(d_all, datetime, pHint_tot_sf_norm4, pH_calc_norm4)
seafet_calc_contros_xts <- as.xts(seafet_calc_contros_xts, order.by = d_all$datetime)
dygraph(seafet_calc_contros_xts, group = "awipev", main="pH calculated vs pH seaFET, normalized at 4°C", ylab="pHT") %>%
    dySeries("pHint_tot_sf_norm4", label = "pH seaFET", color ="blue", strokeWidth=0, pointSize=2) %>%
    dySeries("pH_calc_norm4", label = "pH calculated", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
    # dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
    dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
    dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
    dyRangeSelector(height = 30, dateWindow= NULL)
```
### **Spectro / durafet**

@@

p_sf_spectro <-  ggplot(d_all,aes(x=pHint_tot_sf, y= pH_s_seafet_temp_field, label = month))+
  geom_text( aes(color=factor(month))) + 
  scale_color_discrete(guide = "none")+
  geom_line(aes(x = pH_calc_norm4, y = pH_calc_norm4), linetype = "dashed") +
  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
  labs(title = paste("pH spectro vs pH seaFET","\n Adj R2 = ", signif(fit$rsquare, 3),
                     "; Intercept =", signif(fit$regression.results[2,2], 3),
                     "; Slope =", signif( fit$regression.results[2,3], 3),
                     "; P =", signif(fit$P.param, 3))) +
  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
    coord_fixed(ratio = 1 , xlim=c(8,8.2), ylim=c(8,8.2))+
  labs(x="pH seaFET", y="pH spectro, 4°C ", color = "Months") + theme_bw() 
p_sf_spectro
```
## SNAPO-CO2
Since November 2018, informations on weekly Ferrybox and monthly durafet/seaFET samplings are collected in a online document that can be consulted at anytime:

>>>>

seafet_calc_contros_xts <- dplyr::select(d_all, datetime, pHint_tot_sf_norm4, pH_calc_norm4)
seafet_calc_contros_xts <- as.xts(seafet_calc_contros_xts, order.by = d_all$datetime)
dygraph(seafet_calc_contros_xts, group = "awipev", main="pH calculated vs pH seaFET, normalized at 4°C", ylab="pHT") %>%
    dySeries("pHint_tot_sf_norm4", label = "pH seaFET", color ="blue", strokeWidth=0, pointSize=2) %>%
    dySeries("pH_calc_norm4", label = "pH calculated", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
    # dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
    dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
    dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
    dyRangeSelector(height = 30, dateWindow= NULL)
```

### **Spectro / durafet**

@@

p_sf_spectro <-  ggplot(d_all,aes(x=pHint_tot_sf, y= pH_s_seafet_temp_field, label = month))+
  geom_text( aes(color=factor(month))) + 
  scale_color_discrete(guide = "none")+
  geom_line(aes(x = pH_calc_norm4, y = pH_calc_norm4), linetype = "dashed") +
  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
  labs(title = paste("pH spectro vs pH seaFET","\n Adj R2 = ", signif(fit$rsquare, 3),
                     "; Intercept =", signif(fit$regression.results[2,2], 3),
                     "; Slope =", signif( fit$regression.results[2,3], 3),
                     "; P =", signif(fit$P.param, 3))) +
  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
    coord_fixed(ratio = 1 , xlim=c(8,8.2), ylim=c(8,8.2))+
  labs(x="pH seaFET", y="pH spectro, 4°C ", color = "Months") + theme_bw() 
p_sf_spectro
```

## SNAPO-CO2
Since November 2018, informations on weekly Ferrybox and monthly durafet/seaFET samplings are collected in a online document that can be consulted at anytime:
